---
title: "Reading results with the SQLResultsProcessor"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reading results with the SQLResultsProcessor}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  message  = FALSE, 
  results  = "hide", 
  fig.show = "hide",
  eval     = FALSE
)
```

```{r setup}
library(CBM4r)
```

## Getting started

### Initialize the CBM4 virtual environment

```{r use_virtualeenv}
# Use the CBM4 virtual environment
# See `vignette("Getting-started", package = "CBM4r")`
reticulate::use_virtualenv("r-CBM4")
```

### Set CBM4 simulation data source

```{r paths}
# Set CBM4 output data directory path
cbm4_data <- "cbm4_data"
```

All results functions can accept `cbm4_data` or `cbm4_results` as input. 
Most functions will read `cbm4_data` into a `SQLResultsProcessor` object as the first step,
so calling `cbm4_results_processor` directly is more efficient when reading multiple results.

```{r results_processor}
# Get CBM4 SQLResultsProcessor
cbm4_results <- cbm4_results_processor(cbm4_data)
```

## Read results

See the [CBM4 SQL Results Processor documentation](https://github.com/cat-cfs/tech_docs/blob/main/dev/cbm4/results/sql_results_processor.md) for more information about the `SQLResultsProcessor`.

### Direct query the SQL Results Processor

```{r results_query}
# See list of available views to query
data.table::as.data.table(cbm4_results$views)[, c("name", "column_names")]

# Example: get cohort pool totals in the first and last timesteps
cbm4_results_query(cbm4_results, "SELECT * FROM spatial_pool_indicators WHERE timestep == 1 ORDER BY raster_index")
cbm4_results_query(cbm4_results, "SELECT * FROM spatial_pool_indicators WHERE timestep == (SELECT MAX(timestep) FROM simulation) ORDER BY raster_index")

# Example: get cohort pool summaries in the first and last timesteps
cbm4_results_query(cbm4_results, "SELECT * FROM spatial_composite_pool_indicators WHERE timestep == 1 ORDER BY raster_index")
cbm4_results_query(cbm4_results, "SELECT * FROM spatial_composite_pool_indicators WHERE timestep == (SELECT MAX(timestep) FROM simulation) ORDER BY raster_index")
```

### Results by timestep

```{r results_totals}
# See list of views that can be read into a summary table
cbm4_results_totals(cbm4_results, list = TRUE)

# Read pools totals by timestep
cbm4_results_totals(
  cbm4_results,
  view_name = "composite_pool_indicators",
  units     = "t"
)
cbm4_results_totals(
  cbm4_results,
  view_name = "composite_pool_indicators",
  units     = "Mt"
)

# Read flux totals by timestep
cbm4_results_totals(
  cbm4_results,
  view_name = "composite_flux_indicators",
  units     = "t"
)
cbm4_results_totals(
  cbm4_results,
  view_name = "composite_flux_indicators",
  units     = "Mt"
)
```

### Results by pixel

```{r results_raster}
# See list of views with columns that can be read into a a raster
cbm4_results_raster(cbm4_results, list = TRUE)

# Read Net Primary Productivity (NPP) raster
rastNPP <- cbm4_results_raster(
  cbm4_results, 
  view_name   = "spatial_composite_flux_indicators",
  view_column = "Ecosystem Indicators - Productivity - Net Primary Productivity (NPP)",
  timesteps   = 1:2
)
terra::plot(
  rastNPP,
  main       = c("timestep 1: NPP (tC/ha)", "timestep 2: NPP (tC/ha)"),
  type       = "continuous",
  col        = colorRampPalette(c("lightgreen", "darkgreen"))(10),
  breaks     = seq(0, ceiling(max(terra::values(rastNPP), na.rm = TRUE)), length.out = 10),
  background = "darkgrey",
  axes       = FALSE
)
```

### Study area grid

```{r results_grid}
# Get study area grid
cbm4_results_grid(cbm4_results)

# Get study area chunk processing key
cbm4_results_grid_key(cbm4_results)
```

